Bootstrap_draft

### 2024-07-03 Bootstrap_draft.Rmd
BCa and grid not finished

---
title: "Bootstrap"
output: pdf_document
date: "2024-06-26"
---

@@

((We do not need the artificial forest for now. We just need a virtual 1000x1000 square.))

@@

# Sample size
n <- 100

@@

# Number of bootstrap samples
B <- 500

@@

@@

    call <- match.call()
    # n <- length(x)
    n <- nrow(x)
    # thetahat <- theta(x,...)
    a <- c()
    for (i in 1:n) {
      a <- append(a, circle3_nb(x[i, 1], x[i, 2], 15, 9, 6))
    }
    # Estimated total thus obtained from the initial sample
    thetahat <- sum(a/p)

@@

    # thetastar <- apply(bootsam,1,theta,...)
    thetastar <- c()
    for (c in 1:B) {
      a <- c()
      for (i in 1:n) {
        a <- append(a, theta(bootsam[i, (2*c)-1], bootsam[i, 2*c], 15, 9, 6))
      }
      thetastar <- append(thetastar, sum(a/p))
    }
    thetastar <- sort(thetastar)

@@

    u <- rep(0,n)
    for(i in 1:n){
        # u[i] <- theta(x[-i],...)
        x_i <- x[-i]
        a <- c()
        for (j in 1:n) {
          a <- append(a, theta(x_i[j, 1], x_i[j, 2], 15, 9, 6))
        }
        # Estimated total thus obtained from the initial sample
        u[i] <- sum(a/p)
    }
    uu <- mean(u)-u
    acc <- sum(uu*uu*uu)/(6*(sum(uu*uu))^1.5)

@@

```{r}
bcanon(random_points,bootsam,circle_nb,...,alpha = .95)
```

# With a grid

```{r}
# Is it OK?
```

```{r}

```

>>>>

---
title: "Bootstrap_draft"
output: html_document
date: "2024-07-03"
---

@@

@@

# Sample size
n <- 50

@@

# Number of bootstrap samples
B <- 100

@@

```{r}
# Estimation of the total number of trees for each bootstrap sample
est_boot <- c()
for (c in 1:B) {
  # a <- circle_nb(rbind(df_boot[, (2*c)-1], df_boot[, 2*c], c(rep(R,n))))
  a <- apply(df_boot[, (2*c)-1], df_boot[, 2*c], c(rep(R,n)), MARGIN = 1, FUN = circle_nb)
  est_boot <- append(est_boot, sum(a/p))
}
est_boot <- sort(est_boot)
```

@@

    call <- match.call()
    # n <- length(x)
    n <- nrow(x)
    # thetahat <- theta(x,...)
    a <- c()
    for (i in 1:n) {
      a <- append(a, theta(x[i, 1], x[i, 2]))
    }
    # Estimated total thus obtained from the initial sample
    thetahat <- sum(a/p)

@@

    # thetastar <- apply(bootsam,1,theta,...)
    thetastar <- c()
    for (c in 1:B) {
      a <- c()
      for (i in 1:n) {
        a <- append(a, theta(bootsam[i, (2*c)-1], bootsam[i, 2*c]))
      }
      thetastar <- append(thetastar, sum(a/p))
    }
    thetastar <- sort(thetastar)

@@

    u <- rep(0,n)
    for(i in 1:n){
        # u[i] <- theta(x[-i],...)
        x_i <- x[-i]
        a <- c()
        for (j in 1:n) {
          a <- append(a, theta(x_i[j, 1], x_i[j, 2]))
        }
        # Estimated total thus obtained from the initial sample
        u[i] <- sum(a/p)
    }
    uu <- mean(u)-u
    acc <- sum(uu*uu*uu)/(6*(sum(uu*uu))^1.5)

@@

```{r}
bcanon(random_points,df_boot,circle_nb,alpha = .95)
```
